---
title: "jackie 35"
author: "Zoe Zhou"
date: "07/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Pressure values are records at a frequency of 40 Hz. 
## So 40 measurements per second. 
## 1 measurement every 25 milliseconds. 
## We have missing data in raw `_all.csv` files. But they had been excluded.

```{r}
# Found the folder that contains jackie's session 35 (here we call it jackie 1) data
folder = list.files(pattern = "jackie 35", full.names  = TRUE)

source("Functions.R")
df.list = get.df.list(folder)
```

## Step 1. Have an overall peek at our data
##### One of them maybe ambient data - usually df1 - need to be decided manually. Sometimes data might be broken due to the Bluetooth connection lost.

##### Check temperature
```{r}
lapply(df.list, plot.temp)
```


##### Check Pressure
```{r}
lapply(df.list, myplot)
```

### Comments: Seems like Squeeze and Hold data is located in df1 to df5. We can combine everything first and then maunally segement `Squeeze and hold` exercise out.

#### Mutate new column rectime (recording time) to combine all data frames (except the ambient data - usually df1). Note the *timegap* here is 20 ms. See notes at the top.
```{r}
(whole = combinedf(df.list, timegap = 25))
```

#### Putting Pressure and temperature side by side and have a look
```{r}
side.by.side(pressuredata = whole, tempdata = whole, name = "the whole recording")
```


## Step 2. Remove baseline.
##### Default - take the first n seconds' data (we consider it as the relax period) - can manually change it to 2 - 5 seconds
```{r}
first_n_seconds = choose.baseline(whole, relax.time.length = 5000)
```

#### After removal, take a look at the whole recording with temperature
```{r}
# our dataset called `change` now (since after removal, we have the pressure change for each sensor)
change = baseline(whole, first_n_seconds)

side.by.side(pressuredata = change, tempdata = whole, name = "the whole recording (baseline removed)")

# Save this image to impress your supervisors xD
#ggsave("Whole (with temp).png", width = 10, height = 5)
```


## Step 3. Cut the whole to get Squeeze and Hold (optional).
##### Sometimes need to manually subtract a few seconds before next exercise starts (to get just `Squeeze and hold` data) - e.g. here we subtract another 19 s
Due to the Bluetooth connection lost, we lost some time.
But when we are combining all dfs back together, we mutate a new `rectime` column, which is continuous. If we can come up with a better approach to deal with this lost time, we might not need to manually subtract extra seconds. 

## Step 3. Cut the whole to get Squeeze and Hold (optional).

```{r}
# Check if need to trim
trim.both(folder, change, whole, trim = 19000, plot.both = FALSE)
```

trim 19s, lets plot both temperature and pressure side by side.
```{r}
trim.both(folder, change, whole, trim = 19000, plot.both = TRUE)
#ggsave("Squeeze and hold (with temp).png", width = 10, height = 5)
```



### Comments: The negative values in the graph above were resulted from the sensors. It doesn't mean we removed baseline values wrongly.
### When the sensors were being contracted  by the muscles around, they were being sucked, and might be stuck for a bit. After contraction, the muscle relaxed ( during the rest time), the sensors were trying to go back to its original place *slowly.* Hence we observe not always just a flat line (e.g red, pink sensors in the graph above), instead some of the sensors slowly jumped back from negative to 0. (e.g. The green, orange and purple in the graph above)


## Step 4. Prepare for segmentation.
##### If good - Peak pressure trace?
```{r}
change = get.peak.trace(change)
```

##### If noisy - Can we smooth the peak pressure values? `span` is really important here
```{r}
tidydata = tidy.pressure(change)
smoothed.peak.df = get.smooth.line(tidydata)
```
## Step 4.5. Detect peaks (optional - it picks up small peaks sometimes so it's a bit useless)


Default minpeakdistance = 500 (each contraction last around 5s).
This really depends on the participant (time length of contractions varies! Sometimes 7s, 8s, or 10s)

##### Get the top n peaks from smoothed.peak.df
```{r}
n_peaks = get.peaks(change, smoothed.peak.df, noise.timelength = 5000, minpeakdistance = 500)
```

## Step 5. Segmentation
```{r}
greedy.fit = get.greedy.fit(smoothed.peak.df, n_peaks)
```
#### COMMENTS : Sometimes unnoticeable small red line (a changepoint) occurs around 9000.


Change Q manually to give the best reults
```{r}
greedy.fit = get.greedy.fit(smoothed.peak.df, Q = n_peaks*2-4)
```
## Step 6. Plot
```{r}
# Let's ignore the endurance and the knack for now (the last 8 changepoints excluded)
mypoints = drop.points(greedy.fit, dropfirst = 0, droplast = 8)

# Check how it looks like without shifting
how.to.shift(change, mypoints, n_event = 20)
```
##### Decided to shift starting time of everything (except no.14) 30 points to the left, the ending time of no.14 30 points to the right
```{r}
how.to.shift(change, mypoints, n_event = 20,
             start.go.left = 19:20, start.go.left.size = 30,
             end.go.right = 1:17, end.go.right.size = 50)
```

##### Now they should look perfect and ready to be saved
```{r}
# how.to.shift(change, mypoints, n_event = 20, save = TRUE,
#              start.go.left = 19:20, start.go.left.size = 30,
#              end.go.right = 1:17, end.go.right.size = 50)

```



## Step 7. Average out

```{r}
contraction.df = get.contraction.df(change, mypoints, n_pfmc = 20, drop.start = 1000, drop.end = 500)
get.averaged.plot(contraction.df) #, save = TRUE)
```








