---
title: "jenny 114"
author: "Zoe Zhou"
date: "17/02/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Pressure values are records at a frequency of 50 Hz. 
## So 50 measurements per second. 
## 1 measurement every 20 milliseconds. 

## The femfit is placed backwards.

```{r}
# Found the folder that contains jenny data
folder = list.files(pattern = "jenny 114", full = TRUE)
list.files(folder)

```

```{r}
(all.csv = list.files(folder, pattern = ".csv$", full.names = TRUE))
all.csv = all.csv[-grep("all", all.csv)]
```

### Getting information in JSON file (the timestamps where the exercise was selected - these can help our segementation process)
```{r}
source("Functions.R")
session = unlist(fromJSON(file = list.files(path = folder, pattern = "session.json", recursive = TRUE, full.names = TRUE)))
# Find all exercise names
lines = grep("exercise selected", session)

exercise.string = unname(session[lines])

# Find where `Squeeze and hold` exercise info locate in exercise.string

squeeze_and_hold_exercise_order = grep("Squeeze and Hold", exercise.string)
squeeze_and_hold_line = lines[squeeze_and_hold_exercise_order]


# Strangely, We have 2 squeeze_and_hold_indices
# Check if "Pause" had been pressed between this 2 selection
# If Paused, take the second one as the squeeze_and_hold start time
if (length(squeeze_and_hold_line) > 1) {
  if (any(grepl("Pause", session[squeeze_and_hold_line[1]:squeeze_and_hold_line[2]]))) {
  squeeze_and_hold_line = squeeze_and_hold_line[2]
  squeeze_and_hold_exercise_order = squeeze_and_hold_exercise_order + 1
  }
}


# The next line is the time information
squeeze_and_hold_start_time = as.numeric(session[squeeze_and_hold_line + 1])

# Find where next exercise info locate in exercise.string
next_exercise_name = exercise.string[squeeze_and_hold_exercise_order + 1]
next_exercise_line = lines[squeeze_and_hold_exercise_order + 1]
# The next line is the time information
next_start_time = as.numeric(session[next_exercise_line + 1])

```


### Read in all data 
```{r}
df.list = lapply(all.csv, read.csv)

names(df.list) = paste0("df", 1:length(df.list))
```

### A helper function that define the column names for each df
```{r}
define.col = function(df) {
  colnames(df) = c("rectime", paste0("p", 1:8), paste0("t", 1:8))
  df
}
```

### Define the column names for all dfs
```{r}
df.list = lapply(df.list, define.col)
```


### Check temperature

```{r}
lapply(df.list, plot.temp)
```

### Check Pressure

```{r}
lapply(df.list, plot2)
```

```{r}
whole = df.list[[3]]
```


## Remove baseline values using the first 3 seconds' data (we consider it as the relax period)
```{r}
first3seconds = whole %>% filter(rectime < 3000)

plot2(first3seconds, name = "first 3 seconds")
```

### Look at the whole recording with temperature
```{r}
change = baseline(whole, first3seconds)
p = myplot(change, name = "the whole recording (baseline removed)")
t = plot.temp(whole, name = "the whole recording (baseline removed)")
ggarrange(p + rremove("xlab"), 
                   t,
                    ncol = 1, nrow = 2, align = "v", 
                   common.legend = TRUE, legend = "right")
```


## Segementation (if needed)
### Manually sectioned bb seconds before `Rapid Contractions` starts (to get just `Squeeze and hold`)
```{r}
p = change %>% filter(rectime < (next_start_time - squeeze_and_hold_start_time)) %>%
  myplot(name = "Squeeze and hold") + theme_classic()

t = whole %>% filter(rectime < (next_start_time - squeeze_and_hold_start_time)) %>%
  plot.temp(name = "Squeeze and hold") + theme_classic()

ggarrange(p + rremove("xlab"), 
                   t,
                    ncol = 1, nrow = 2, align = "v", 
                   common.legend = TRUE, legend = "right")

#ggsave("Temp.png", width = 10, height = 5)

```

### Comments: The negative values in the graph above were resulted from the sensors. It doesn't mean we removed baseline values wrongly.
### When the sensors were being contracted  by the muscles around, they were being sucked, and might be stuck for a bit. After contraction, the muscle relaxed ( during the rest time), the sensors were trying to go back to its original place *slowly.* Hence we observe not always just a flat line (e.g red, green sensors in the graph above), instead some of the sensors slowly jumped back from negative to 0. (e.g. The yellow, orange and purple in the graph above)



### Get the peak pressure values
```{r}
change$peak = apply(change[, paste0("p", 1:8)], 1, max)
```

## Individual PFMCs

### Emphasize the peaks
```{r}
plot2(change, name = "the whole recording") + geom_line(aes(x = rectime, y = peak), col = "black")
```


### Can we smooth the peak pressure values? `span` is really important here!!!!!!!!!!
```{r}
tidydata = tidy(change)
lo.whole = loess(peak ~ rectime, data = tidydata, span = 0.01)
plot(tidydata$rectime, tidydata$peak, pch = 21, cex = 0.5)

lines(tidydata$rectime[order(tidydata$rectime)],
      predict(lo.whole)[order(tidydata$rectime)],
      col = "red", lwd = 2)
```

### Get smoothed.peak.df - can be used in the peaks and changepoints detection later (sometimes give better results)
```{r}

smoothed.peak.df = unique(data.frame(rectime = tidydata$rectime[order(tidydata$rectime)], 
                            peak = predict(lo.whole)[order(tidydata$rectime)]))
smoothed.peak.df$id = 1:nrow(smoothed.peak.df)

# Plot the smooth line
ggplot(data = tidydata) +
  geom_line(aes(x = rectime, y = pressure, color = sensor)) +
  geom_line(data = smoothed.peak.df, aes(x = rectime, y = peak), size = 1) +
  labs(x = "Recording Time (in s)", y = "Pressure Change (in mm Hg)",
       title = "Pressure trace from all sensors with smoothed line of peak") + 
    scale_color_brewer(palette = "Set1") + 
  guides(color = guide_legend(override.aes = list(size = 5)))

#ggsave("Colored Pressure traces with Smoothed Line.png", width = 10, height = 4)
```

### Get the top n peaks.

## Before calling `findpeaks` function, set a threshold called noise to be ignored (not picked up as a peak - a potential event)
```{r}
# Get the baseline noise from the first 5 seconds of data
noise = change %>% 
  tidy() %>%
  filter(rectime < 5000) %>%
  summarise(maxdiff = max(pressure) - min(pressure)) %>%
  as.numeric()

change %>%
  filter(rectime < 5000) %>% plot2()
```

#### Decided not to use smoothed.peak.df, original peak data works very well.

#### Note: changed minpeakdistane to 700 !!!!! Depends on the participant (time interval between contractions varies!!!!!!!!!!)
```{r}
top_n_peaks = findpeaks(smoothed.peak.df$peak, minpeakdistance = 700, minpeakheight = noise)
top_n_peaks_indices = sort(top_n_peaks[, 2])

### Check how many peaks we got
(n_peaks = length(top_n_peaks_indices))
```

### Comments: n_peaks ideally should = 26, since we have 20 PFMCs in `squeeze and hold`, 2 rapids, 2 endurance and 2 knacks. But very often, the first bump in endurance exercise will be picked up as a peak. See graph below.


```{r}
plot(smoothed.peak.df$peak, type = "l")
points(top_n_peaks[, 2], top_n_peaks[, 1], pch = 15, col = "red")
text(top_n_peaks[, 2] + 300, top_n_peaks[, 1] + 2, as.character(top_n_peaks[, 2]))
```

### Greedy method ###
#### Trying to get  `n_peaks*2` change points at once using Binary Segementation, `Q` has been manually changed to give the best results. 
```{r}
all.binseg = cpt.mean(smoothed.peak.df$peak, method = "BinSeg", Q = n_peaks*2-5)
greedy.fit = cpts(all.binseg)
```

```{r}
param.est(all.binseg)
```


```{r}
plot(all.binseg)
```

### Doing pretty well for pfmcs, not too good for endurance and the knack.

```{r}
greedy.fit
```


## For whole data (8 sensors) - Back to our original data
```{r}
# Let's ignore the endurance and the knack for now (the last 8 changepoints excluded)
mypoints = greedy.fit[1:(length(greedy.fit)-19)]
raw.start.end.rectime = change$rectime[mypoints] 

n_event = 30
```

## Just double check if we actually get the changepoints right (can manually modify a bit here if needed)
```{r}

event_start = seq(1, n_event, 1)*2 - 1

event_end = seq(1, n_event, 1)*2

# Shift the ending time of Contraction NO.1 - 11, and NO.29 in exercise`Squeeze and hold` 30 points to the right (so the graph looks nicer)
mypoints[event_end[c(1:11, 29)]] = mypoints[event_end[c(1:11, 29)]] + 50


# Shift the starting time of all pfmcs in exercise `Squeeze and hold` 50 points to the left (so the graph looks nicer)
mypoints[event_start[c(13:29)]] = mypoints[event_start[c(13:29)]] - 50

mypoints[event_start[c(4, 12, 18, 21, 30)]] = mypoints[event_start[c(4, 12, 18, 21, 30)]] - 30

# Shift the starting time of Contraction NO.18, 21, 28, 29 in exercise `Squeeze and hold` 10 points to the left (so the graph looks nicer)
#mypoints[event_start[c(4, 6, 8, 10, 30)]] = mypoints[event_start[c(4, 6, 8, 10, 30)]] - 50

# # Shift the ending time of Contraction NO.1 - 11, and NO.29 in exercise`Squeeze and hold` 30 points to the right (so the graph looks nicer)
# mypoints[event_end[c(4, 29)]] = mypoints[event_end[c(4, 29)]] + 10

start.end.rectime = change$rectime[mypoints] 

# plot2(change) + theme_void() + 
#   geom_vline(xintercept = start.end.rectime)

```

## Let's have a look at each individual event (just in squeeze and hold & rapids) !!!!
```{r}
for (i in 1:n_event) {
  start = start.end.rectime[i*2 - 1]
  end = start.end.rectime[i*2]
  
print(myplot(getsubdata(change, start, end), name = paste0("Event No.", i)) + 
          theme_classic() +
          theme(axis.text = element_text(face = "bold", size = 14),
                axis.title = element_text(face = "bold", size = 14)))
  
  ggsave(paste0("Event No.", i, ".png"), height = 5, width = 8)
}

```



### Dropping the starting (1.5s) and ending (1.5s) baseline data for each contraction
```{r}
contraction.data = list()
for (i in 1:n_event) {
    contraction.data[[i]] = getsubdata(change, start.end.rectime[i*2 - 1] + 1500, start.end.rectime[i*2] - 1500)
    print(myplot(contraction.data[[i]], name = paste0("Contraction No.", i)) + 
          theme_classic())
  }
```

### Mutate a new column `contration id` for each contraction data, then combine all together
```{r}
for (i in 1:length(contraction.data)) {
  contraction.data[[i]] = contraction.data[[i]] %>% 
    mutate(contraction = as.factor(i))
}

contraction.df = do.call("rbind", contraction.data)
head(contraction.df)
```

### Averaging each contraction for each sensor

```{r}
avged.df = contraction.df %>% 
  tidy() %>% 
  group_by(contraction, sensor) %>% 
  summarise(mean = mean(pressure), sd = sd(pressure, na.rm = TRUE))

ggplot(data = avged.df, aes(x = contraction, y = mean, group = sensor, color = sensor)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.2) +
  labs(title = "Mean Pressure over contraction", y = "Mean pressure (mmHg)", x = "Contraction",
       subtitle = "Jenny session 114") +
  theme_classic() +
  scale_color_brewer(palette = "Set1")


#ggsave("Mean pressure for each sensor over contraction.png", width = 10, height = 5)

```





### Endurance and the knack
```{r}

where_rapids_end = mypoints[length(mypoints)]

endurance_and_knack = getsubdata(change, start = change$rectime[where_rapids_end], stop = max(change$rectime))

plot2(endurance_and_knack, name = "The rest")
```









