---
title: "femfit-main"
author: "Zoe Zhou"
date: "10/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Zip folders are downloaded from the femfit website straight away.
DATA files are from the recording device. 
CSV files with names ending like *_all.csv* contains all data which have missing values.  
CSV files with names ending like .csv contains data after removing NAs.

----------------------------------------- TASK -----------------------------------------------
We are looking for the peak pressure values among three contractions, to find which one(or more than one) sensors best represents the active pelvic muscles. We are particularly interested in the variability of the result.

***************************************** Note *********************************************
Each pressure measurement includes the __baseline atmosphere pressure__ due to the great sensitivity of the sensors. We decided to exclude this baseline value during the investigation. Here we are taking a relatively stable resting period, usually before contractions happen.

All the time-stamps for each exercise, are recorded manually by the user, saved in JSON files. 

 - For Jenny and Jackie's data, they are using the newest device, (e.g. Jackie is using device _FF400059_). 
 - Pressure values are records at a frequency of 50 Hz.
 - So 50 measurements per second. We have 1 measurement every 20 milliseconds. 
 - iPhone 7 (Jackie) has something strange happening, which records at frequency of 40 Hz, so 1 measurement every 25 ms.


for *Kari bo* study (a bit old), We were using device _pfd0084_ , which records measurements at a frequency of  __100 Hz__. 
So we have 100 measurements per second. 1 measurement every 10 milliseconds. 


***
##### Finding baseline: Rough Guess

As each sensor has a different initial pressure value at the start of the PFMC exercise, the patterns of raw pressure traces are not so easy-to-understand. Hence we should remove the baseline pressure values and focus on the changes. Then we can get a better idea of which sensor has the greatest change during the actions.

General Method:
Find a rest period of at least 2 seconds with relatively stable pressure values, average it out for each sensor and treat it as the baseline.

Question:
How to find this *stable rest period*?

Procedure:
We attempted 3 times taking 3 different rest periods. 
Attempt1: Take the first exercise, relax 30 seconds. 

Attempt2: Take all the time before the first contraction. Means when the device started recording, we get rest data, until the participant start to contract.

Attempt3: Take the 15s rest time within the pfmc exercise. 

After taking out the average pressure values for each sensor, all these 3 trials gave very similar output. Regarding to the negative values, they can be explained by the air bubbles in the sensor encapsulation.

However, attempt3 gave the most reliable initial value (closest to 0), so we decided to stick to this approach for all participants.


##### Now call the big nice function and check out the graphic results
```{r}
# Find folders that contain our data
data_folders = list.files(pattern = "_csv")

# Load in all the helper functions
source("Functions.R")

# Get all pfmc data list
pfmcdatalist = lapply(data_folders, process)

# Extract out baseline removed data (named as pfmcchange data) from all 3 participants
pfmcchange.df.list = list()

for (i in 1:length(pfmcdatalist)) {
  pfmcchange.df.list[[i]] = pfmcdatalist[[i]][[4]]
  names(pfmcchange.df.list)[i] = names(pfmcdatalist[[i]])[4]
}
```

### Visualize our data
```{r}
# Initialize empty lists to store all pfmc plots
change.plots = list()
pressure.plots = list()

# Get the plots
for (i in (1:length(pfmcdatalist))) {
  pressure.plot.name = as.character(names(pfmcdatalist[[i]])[3])
  change.plot.name = as.character(names(pfmcdatalist[[i]])[4])
  
  pressure.plots[[i]] = myplot(pfmcdatalist[[i]][[3]], name = pressure.plot.name)
  
  names(pressure.plots)[[i]] = pressure.plot.name
  
  change.plots[[i]] = myplot(pfmcdatalist[[i]][[4]], name = change.plot.name)
  
  names(change.plots)[[i]] = change.plot.name
}

# Look at the plots
print(change.plots)
print(pressure.plots)
```


```{r eval = FALSE}
# Save the plots
# invisible(mapply(ggsave, width = 10, height = 4, dpi = 300,
#                  file = paste0(names(change.plots), ".png"), plot = change.plots))

```


