### Non-greedy (Patience is virtue) method ###
#### Segment1 is from the start to the 1st peak. Return the 1st peak start point. (point 1)
```{r}
seg1.test = cpt.mean(data[1:top_3_peaks_indices_p1[1], "p1"])
point1 = cpts(seg1.test)
plot(seg1.test)
text(cpts(seg1.test), 0, cpts(seg1.test), font = 2)
```
#### Segment2 is from point1 to the 2nd peak. Return the 1st peak end point. (point 2)

#### Need to change the x axis
```{r}
seg2.test = cpt.mean(data[point1:top_3_peaks_indices_p1[2], "p1"])
point2 = cpts(seg1.test) + cpts(seg2.test)
plot(seg2.test)
text(cpts(seg2.test), 0, point2, font = 2)
```
#### Segment3 is from point2 to 2nd peak. Return the 2nd peak start point. (point 3)

#### Need to change the x axis
```{r}
seg3.test = cpt.mean(data[point2:top_3_peaks_indices_p1[2], "p1"])
point3 = point2 + cpts(seg3.test)
plot(seg3.test)
text(cpts(seg3.test), -0.5, point3, font = 2)
```

#### Segment4 is from point3 to 3rd peak. Return the 2nd peak end point. (point 4)

#### Need to change the x axis
```{r}
seg4.test = cpt.mean(data[point3:top_3_peaks_indices_p1[3], "p1"])
point4 = point3 + cpts(seg4.test)
plot(seg4.test)
text(cpts(seg4.test), 0, point4, font = 2)
```

#### Segment5 is from point4 to 3rd peak. Return the 3rd peak start point. (point 5)

#### Need to change the x axis
```{r}
seg5.test = cpt.mean(data[point4:top_3_peaks_indices_p1[3], "p1"])
point5 = point4 + cpts(seg5.test)
plot(seg5.test)
text(cpts(seg5.test), 0.5, point5, font = 2)
```

#### Segment6 is from point5 to the end. Return the 3rd peak end point. (point 6)

#### Need to change the x axis
```{r}
seg6.test = cpt.mean(data[point5:nrow(data), "p1"])
point6 = point5 + cpts(seg6.test)
plot(seg6.test)
text(cpts(seg6.test), 0.5, point6, font = 2)
```


################## Automate the process above ##################

#### Get the top 3 peaks first. 
```{r}
top_3_peaks = findpeaks(smoothed.df$pressure, minpeakdistance = 500, npeaks = 3)
top_3_peaks_indices = top_3_peaks[, 2]
plot(smoothed.df$pressure, type = "l")
points(top_3_peaks[, 2], top_3_peaks[, 1], pch = 15, col = "red")
text(top_3_peaks[, 2] + 300, top_3_peaks[, 1], as.character(top_3_peaks[, 2]))
```


Seg 1 - smoothed.df[1:top_3_peaks_indices[1], "pressure"]

Seg 2 - smoothed.df[point1:top_3_peaks_indices[2], "pressure"]

Seg 3 - smoothed.df[point2:top_3_peaks_indices[2], "pressure"]
 
Seg 4 - smoothed.df[point3:top_3_peaks_indices[3], "pressure"]

Seg 5 - smoothed.df[point4:top_3_peaks_indices[3], "pressure"]

Seg 6 - smoothed.df[point5:nrow(smoothed.df), "pressure"]


```{r}
get6points = function(data, y, top_3_peaks_indices){
  start = 1
  
  ends = c(top_3_peaks_indices[1], rep(top_3_peaks_indices[2:3], each = 2), nrow(data))
  
  point = 0
  
  mypoints = list()
  for (i in 1:6) {
    end = ends[i]
    subdata = data[start:end, y]
    seg.test = cpt.mean(subdata)
    
    if (length(cpts(seg.test)) == 0) {
      point = end
    } 
    
    else {
      point = cpts(seg.test) + point
    }
    
    mypoints[[i]] = point
    
    start = point
    
    
    plot(seg.test)
    text(cpts(seg.test), 1, point, font = 2)
    
  }
  
  mypoints
}

```

