
### Start to explore just the PFMC pressure change (baseline removed) for subject s0007
```{r}

# Find all data folders
data_folders = list.files(pattern = "_csv")

# Folder that contains patient3 data s0007
s0007.folder = data_folders[1]

# Load in all the helper functions
source("Functions.R")

# Process folder and get the change dataset for patient 3
data = process(s0007.folder)$pfmcchange.patient3

data$id = 1:nrow(data)
```

## Validating methods - to find 6 change points
#### Let's have a look at sensor 1 traces and its peaks
```{r}
# Set the minimal peak distance to be 100 data points (1 second apart) reference Nadia M. Hamad, 2013
# Set the minimal peak height to be 1 mmHg
peaks_p1 = findpeaks(data$p1,  minpeakheight = 1, minpeakdistance = 100)
plot(data$p1, type = "l")
points(peaks_p1[, 2], peaks_p1[, 1], pch = 15, col = "red")
```

#### Can I set a good threshold to get the TOP 3 peaks (representing 3 contractions) for sensor 1?
```{r}
top_3_peaks_p1 = findpeaks(data$p1, minpeakdistance = 500, npeaks = 3)
top_3_peaks_indices_p1 = top_3_peaks_p1[, 2]
plot(data$p1, type = "l")
points(top_3_peaks_p1[, 2], top_3_peaks_p1[, 1], pch = 15, col = "red")
text(top_3_peaks_p1[, 2] + 250, top_3_peaks_p1[, 1], as.character(top_3_peaks_p1[, 2]))
```
### Non-greedy (Patience is virtue) method ###
```{r}
source("get6points.R")
get6points(data, "p1", top_3_peaks_indices_p1)
```

### Greedy method ###
#### Trying to get the 6 change points(Each contraction's start/end timestamps) for sensor 1
```{r}
library(changepoint)

(p1.binseg = cpt.mean(data$p1, method = "BinSeg", Q = 6))
greedy.fit.p1 = cpts(p1.binseg)

plot(p1.binseg)
```
#### Successfully found the 6 change points for sensor 1
```{r}
greedy.fit.p1
```

#### Trying to get the 6 change points for sensor 2
```{r}
(p2.binseg = cpt.mean(data$p2, method = "BinSeg", Q = 6, minseglen = 500))
plot(p2.binseg)
```

Not working so well due to the negative values at the start. Lets try remove that noise.
```{r}
(p2.binseg2 = cpt.mean(data[1000:nrow(data), "p2"], method = "BinSeg", Q = 6, minseglen = 700))
plot(p2.binseg2)
```
Had to change the "minseglen" to get the perfect change points. Otherwise the function picks up noise around time 3500.


#### Trying to get the 6 change points for sensor 3
```{r}
(p3.binseg = cpt.mean(data$p3, method = "BinSeg", Q = 6, minseglen = 700))
plot(p3.binseg)
```

Not working so well due to the negative values at the start. Lets try remove that noise.
```{r}
(p3.binseg2 = cpt.mean(data[1000:nrow(data), "p3"], method = "BinSeg", Q = 6, minseglen = 500))
plot(p3.binseg2)
```

Not working so well.

#### Comment
After attempts on the whole dataset, we found that change point function worked pretty well for sensor 1, but not really for other sensors. 
The parameters (method used, "PELT" or "BinSeg", value of Q, 6 or 7, ...) needed are not consistent.

Decided to stick to the non-greedy method (default method = "AMOC", at most one change), where we feed in each segment of data to the cpt function (using the top 3 peaks we found), get each change point step by step.

### NOW: Smooth the data out, reduce the effect of the noise.

## For smoothed.df - NOTE: x axis is *rectime* not id (start from 48360 not 1)
```{r}
source("smooth-trial.R")
g.smoothed
```

### Greedy method ###
#### Attempt 1 - Try use "PELT" to get all 6 change points at once.
```{r}
smooth.pelt = cpt.mean(smoothed.df$pressure, method = "PELT", minseglen = 5000)
plot(smooth.pelt)
```

Same problem as before, noise at the start had been picked up.

#### Attempt 2 - Try use "BinSeg" to get all 6 change points at once.
```{r}
smooth.binseg <- cpt.mean(smoothed.df$pressure, method = "BinSeg", Q = 6, minseglen = 5000)
plot(smooth.binseg)
```

Using "BinSeg" did not solve the problem. 

#### Attempt 3 - removed the first 10s of the data. Use "PELT" to get all 6 points.

##### Need to change x axis
```{r}
smooth.pelt2 = cpt.mean(smoothed.df$pressure[10000:nrow(smoothed.df)], method = "PELT", minseglen = 5000)
plot(smooth.pelt2)
```

#### Results 5 rectime timestamps + 1 the end point
```{r}
c(cpts(smooth.pelt2) + 10000 + min(smoothed.df$rectime), max(smoothed.df$rectime))
```
It worked ok. But the parameter "minseglen" is really specific.

#### Attempt 4 - removed the first 10s of the data. Use "BinSeg" to get all 6 points.
```{r}
smooth.binseg2 <- cpt.mean(smoothed.df$pressure[10000:nrow(smoothed.df)], method = "BinSeg", Q = 5, minseglen = 4000)
plot(smooth.binseg2)
```
#### Results 5 rectime timestamps + 1 the end point
```{r}
c(cpts(smooth.binseg2) + 10000 + min(smoothed.df$rectime), max(smoothed.df$rectime))
```

To get the results, once again, we switched around the parameter values. When apply this to another patient, it might not work so well as we need to manually change the values of "Q" and "minseglen."

### Non-greedy (Patience is virtue) method ###
```{r}
#### Get the top 3 peaks first. 
top_3_peaks = findpeaks(smoothed.df$pressure, minpeakdistance = 500, npeaks = 3)
top_3_peaks_indices = top_3_peaks[, 2]
plot(smoothed.df$pressure, type = "l")
points(top_3_peaks[, 2], top_3_peaks[, 1], pch = 15, col = "red")
text(top_3_peaks[, 2] + 250, top_3_peaks[, 1], as.character(top_3_peaks[, 2]))

source("get6points.R")
mypoints = get6points(smoothed.df, "pressure", top_3_peaks_indices)

```

Now we have our 6 points!!!!!!!!!!!!!!!!!!! YAH  !!!!!!!!!!!!!!

## For whole data (8 sensors) - Back to our original data
```{r}
start.end.rectime = smoothed.df$rectime[unlist(mypoints)]
```

## Let's have a look at each individual contraction !!!!

```{r}
for (i in 1:3) {
  start = start.end.rectime[i*2 - 1]
  end = start.end.rectime[i*2]
  print(myplot(getsubdata(data, start, end), name = paste0("pfmc no.", i)))
  print(plot2(getsubdata(data, start, end), name = paste0("pfmc no.", i)))
}

```
## Lets write everything in one function
```{r}
zoompfmc = function(data){
  # Load in all the helper functions
  source("Functions.R")

  # Get our smoothed df
  tidydata = tidy(data)
  lo.whole = loess(pressure ~ rectime, data = tidydata, span = 0.1)
  smoothed.df = unique(data.frame(rectime = tidydata$rectime[order(tidydata$rectime)], 
                            pressure = predict(lo.whole)[order(tidydata$rectime)]))
  
  # Get the top 3 peaks indices
  top_3_peaks = findpeaks(smoothed.df$pressure, minpeakdistance = 500, npeaks = 3)
  top_3_peaks_indices = top_3_peaks[, 2]

  source("get6points.R")
  
  # Get our change points
  mypoints = get6points(smoothed.df, "pressure", top_3_peaks_indices)
  start.end.rectime = smoothed.df$rectime[unlist(mypoints)]
  
  # Print our individual PFMCs
  for (i in 1:3) {
    start = start.end.rectime[i*2 - 1]
    end = start.end.rectime[i*2]
    print(myplot(getsubdata(data, start, end), name = paste0("pfmc no.", i)))
    print(plot2(getsubdata(data, start, end), name = paste0("pfmc no.", i)))
  }
}

zoompfmc(pfmcchange.df.list$pfmcchange.patient3)
```

