---
title: "s0009"
author: "Zoe Zhou"
date: "31/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Found the folder that contains patient data s0009
folders = list.files(pattern = "_csv")
folder = folders[grep("_9_", folders)]

# Process the folder, get df.list (containing 3 datasets)
source("Functions.R")
df.list = process(folder)
data = df.list[[1]]
```


```{r}
myplot(data, name = names(df.list)[1])

# Check where is the crazy data (> 800) at the end
end = round(grep("FALSE", data[-1] < 800)[1] / 8)

# Get rid of that crazy part and plot
data[1:(end-50), ] %>% myplot(name = names(df.list)[1])
```

##### Remove the baseline and plot the whole
```{r}
myplot(df.list[[2]][1:(end-50), ], name = names(df.list)[2])
```

##### Get the pfmc data and plot it
```{r}
myplot(df.list[[3]], name = names(df.list)[3])
```
##### Remove the baseline and plot it
```{r}
myplot(df.list[[4]], name = names(df.list)[4])
```

##### Create a new time variable, and add a axis labelling in seconds
---Create a new time variable , by subtracting the recording time variable by its starting time (the minimal value)

```{r}
pfmcdata = df.list[[3]]
pfmcdata$time = pfmcdata$rectime - min(pfmcdata$rectime)
```

---Note, there are some missingness in the data (time gap is not always 10 ms) 

** This might cause a slipperage in data (a drastic drop)

** E.g. TIME = 50 to 90 time gap is 40ms, we lost the data in between **
```{r}
recno = ifelse(diff(pfmcdata$rectime) == 10, "good", NA)
# Give the last one NaN
pfmcdata$isna = as.factor(c(recno, NaN))
summary(pfmcdata$isna)
```

Apparently, we have 90 missing values. But so far, it does not affect our plotting.

### For PFMC change data, we wanna dive closer to see each contraction
### To get smoothed.peak.df to reduce the effect of noise (the smoothed line captures the pattern of trace fairly well)

## Get the peak pressure values
```{r}
change = df.list[[4]]
change$peak = apply(change[, 1:8], 1, max)
```

## Smooth the peak  `span` is really important here!!!!!!!!!!

```{r}
tidydata = tidy(change)
lo.whole = loess(peak ~ rectime, data = tidydata, span = 0.1)
plot(tidydata$rectime, tidydata$peak, pch = 21, cex = 0.5)

lines(tidydata$rectime[order(tidydata$rectime)],
      predict(lo.whole)[order(tidydata$rectime)],
      col = "red", lwd = 2)
```




```{r}
# Get smoothed.peak.df
smoothed.peak.df = unique(data.frame(rectime = tidydata$rectime[order(tidydata$rectime)], 
                            peak = predict(lo.whole)[order(tidydata$rectime)]))
smoothed.peak.df$id = 1:nrow(smoothed.peak.df)

# Plot the smoothed peak line
ggplot(data = tidydata) +
  geom_line(aes(x = rectime, y = pressure, color = sensor)) +
  geom_line(data = smoothed.peak.df, aes(x = rectime, y = peak), size = 1) +
  labs(x = "Recording Time (in s)", y = "Pressure Change (in mm Hg)",
       title = "Pressure trace from all sensors with smoothed line of peak") + 
    scale_color_brewer(palette = "Set1") + 
  guides(color = guide_legend(override.aes = list(size = 5)))

```


#### Get the top n peaks.

## Before calling `findpeaks` function, set a threshold called noise to be ignored (not picked up as a peak - a potential event)
```{r}
# Get the baseline noise from the first 15 seconds of data
noise = change %>% 
  tidy() %>%
  filter(rectime < (min(change$rectime) + 15000)) %>%
  summarise(maxdiff = max(pressure) - min(pressure)) %>%
  as.numeric()

change %>%
  filter(rectime < (min(change$rectime) + 15000)) %>% plot2()
```


#### Note: changed minpeakdistane to 500 !!!!! Depends on the participant (time interval between contractions varies!!!!!!!!!!)
```{r}
top_n_peaks = findpeaks(smoothed.peak.df$peak, minpeakdistance = 500, minpeakheight = noise)
top_n_peaks_indices = sort(top_n_peaks[, 2])

### Check how many peaks we got
(n_peaks = length(top_n_peaks_indices))
```


```{r}
plot(smoothed.peak.df$peak, type = "l")
points(top_n_peaks[, 2], top_n_peaks[, 1], pch = 15, col = "red")
text(top_n_peaks[, 2] + 300, top_n_peaks[, 1], as.character(top_n_peaks[, 2]))
```

### Greedy method ###
#### Trying to get  `n_peaks*2` change points at once using Binary Segementation, manually choose Q = 6

```{r}
all.binseg = cpt.mean(smoothed.peak.df$peak, method = "BinSeg", Q = 6)
plot(all.binseg)
```



### Doing pretty well!!!!!!!!!! Good job greedy!!!!

```{r}
(greedy.fit = cpts(all.binseg))
```


## For whole data (8 sensors) - Back to our original data
```{r}
mypoints = greedy.fit
n_PFMC = 3
raw.start.end.rectime = change$rectime[mypoints] 

```

## Just double check if we actually get the changepoints right (can manually modify a bit here if needed)
```{r}
pfmc_start = seq(1, n_PFMC, 1)*2 - 1

pfmc_end = seq(1, n_PFMC, 1)*2

# Shift the ending time of contraction no.1, 50 points to the right (so the graph looks nicer)
mypoints[pfmc_end[1]] = mypoints[pfmc_end[1]] + 100

# Shift the starting time of contraction no.2 and no.3, 50 points to the left (so the graph looks nicer)
mypoints[pfmc_start[2:3]] = mypoints[pfmc_start[2:3]] - 100

start.end.rectime = change$rectime[mypoints] 

plot2(change) + theme_void() +
  geom_vline(xintercept = start.end.rectime)

```

## Let's have a look at each individual event (a PFMC) !!!!

```{r}
for (i in 1:n_PFMC) {
  start = start.end.rectime[i*2 - 1]
  end = start.end.rectime[i*2]
  
print(myplot(getsubdata(change, start, end), name = paste0("PFMC No.", i)) + 
          theme_classic())
          # theme(axis.text = element_text(face = "bold", size = 14),
          #       axis.title = element_text(face = "bold", size = 14)))
  
  #ggsave(paste0("Event No.", i, ".png"), height = 5, width = 8)
}

```


### Dropping the starting (1s) and ending (2s) baseline data for each contraction
```{r}
contraction.data = list()
for (i in 1:n_PFMC) {
    contraction.data[[i]] = getsubdata(change, start.end.rectime[i*2 - 1] + 1000, start.end.rectime[i*2] - 2000)
    print(myplot(contraction.data[[i]], name = paste0("Contraction No.", i)) + 
          theme_classic())
  }
```



### Mutate a new column `contration id` for each contraction data, then combine all together
```{r}
for (i in 1:length(contraction.data)) {
  contraction.data[[i]] = contraction.data[[i]] %>% 
    mutate(contraction = as.factor(i))
}

contraction.df = do.call("rbind", contraction.data)
head(contraction.df)
```

### Averaging each contraction for each sensor

```{r}
avged.df = contraction.df %>% 
  tidy() %>% 
  group_by(contraction, sensor) %>% 
  summarise(mean = mean(pressure), sd = sd(pressure, na.rm = TRUE))

ggplot(data = avged.df, aes(x = contraction, y = mean, group = sensor, color = sensor)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.2) +
  labs(title = "Mean Pressure over contraction", y = "Mean pressure (mmHg)", x = "Contraction",
       subtitle = "Participant s0007") +
  theme_classic() +
  scale_color_brewer(palette = "Set1")


#ggsave("Mean pressure for each sensor over contraction.png", width = 10, height = 5)

```


