---
title: "s0007"
author: "Zoe Zhou"
date: "10/12/2019"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Found the folder that contains patient data s0007
folders = list.files(pattern = "_csv")
folder = folders[grep("_7_", folders)]

# Process the folder, get df.list (containing 3 datasets)
source("Functions.R")
df.list = process(folder)
data = df.list[[1]]

# Check where is the crazy data at the end
end = grep("FALSE", data[-1] < 800)[1]

# Get rid of that crazy part and plot
data[1:(end-50), ] %>% myplot(name = names(df.list)[1])
```
##### Remove the baseline and plot the whole
```{r}
myplot(df.list[[2]][1:(end-50), ], name = names(df.list)[2])
```

##### Get the pfmc data and plot it
```{r}
myplot(df.list[[3]], name = names(df.list)[3])
#ggsave("PFMC.png", width = 10, height = 5)
```
##### Remove the baseline and plot it
```{r}
myplot(df.list[[4]], name = names(df.list)[4])
ggsave("PFMC change.png", width = 10, height = 5)
```

##### Create a new time variable, and add a axis labelling in seconds
---Create a new time variable , by subtracting the recording time variable by its starting time (the minimal value)

```{r}
pfmcdata = df.list[[3]]
pfmcdata$time = pfmcdata$rectime - min(pfmcdata$rectime)
```

---Note, there are some missingness in the data (time gap is not always 10 ms) 

** This might cause a slipperage in data (a drastic drop)

** E.g. TIME = 1640	 to 1680 time gap is 40ms, we lost the data in between **
```{r}
recno = ifelse(diff(pfmcdata$rectime) == 10, "good", NA)
# Give the last one NaN
pfmcdata$isna = as.factor(c(recno, NaN))
summary(pfmcdata$isna)
```

Apparently, we have 15 missing values. But so far, it does not affect our plotting.













